---
title: "cleaning-Jiajing"
author: "Jiajing"
date: "11/16/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## import data


```{r}
library(readr)
feature <- read_csv("feature_JJC.csv")
nrow(feature)
dim(feature)
```

##"SalePrice"   
```{r}
sum(is.na(feature$SalePrice)) 
summary(feature$SalePrice)
#csv1
feature1 = feature
#csv2
feature2 = feature1
```

##"1stFlrSF"  
First Floor square feet
```{r}
sum(is.na(feature$"1stFlrSF")) 
summary(feature$"1stFlrSF")
class(feature$"1stFlrSF")
feature1$"1stFlrSF" = as.numeric(feature$"1stFlrSF")
feature2$"1stFlrSF" = as.numeric(feature2$"1stFlrSF")
```
-no NA
-good


##"2ndFlrSF"  
Second floor square feet
```{r}
sum(is.na(feature$"2ndFlrSF")) 
summary(feature$"2ndFlrSF")
sum(feature$"2ndFlrSF" == 0) 
feature1$"2ndFlrSF" = as.numeric(feature$"2ndFlrSF")
feature2$"2ndFlrSF" = as.numeric(feature2$"2ndFlrSF")

```
-no NA
-1668 0

##"3SsnPorch"  
Three season porch area in square feet
```{r}
sum(is.na(feature$"3SsnPorch")) 
sum(feature$"3SsnPorch" == 0) 
#csv1
feature1$"3SsnPorch"= as.numeric(feature1$"3SsnPorch")
feature2$"3SsnPorch"= as.numeric(feature2$"3SsnPorch")
```

-no NA
-2882 0


##"Alley"       
Type of alley access to property

       Grvl	Gravel
       Pave	Paved
       NA 	No alley access
		
```{r}
sum(is.na(feature$Alley)) 
#csv2
```
- 2721 Missing, which means No alley access, should be divided to categories
- good

##"BedroomAbvGr"
```{r}
sum(is.na(feature$BedroomAbvGr)) 
sum(feature$"BedroomAbvGr" == 0) 
class(feature$BedroomAbvGr)
feature1$BedroomAbvGr = as.numeric(feature1$BedroomAbvGr)
feature2$BedroomAbvGr = as.numeric(feature2$BedroomAbvGr)
```
- no NA
- good

##"BldgType"  
 Type of dwelling
		
       1Fam	Single-family Detached	
       2FmCon	Two-family Conversion; originally built as one-family dwelling
       Duplx	Duplex
       TwnhsE	Townhouse End Unit
       TwnhsI	Townhouse Inside Unit
```{r}
sum(is.na(feature$BldgType)) 
summary(feature$"BldgType") 
```
-no NA
-catagorical data

##"BsmtCond"     
Evaluates the general condition of the basement

       Ex	Excellent
       Gd	Good
       TA	Typical - slight dampness allowed
       Fa	Fair - dampness or some cracking or settling
       Po	Poor - Severe cracking, settling, or wetness
       NA	No Basement
```{r}
sum(is.na(feature$BsmtCond)) 
```
- NA is no Basement.
- Catagory data

##"BsmtExposure" 

Refers to walkout or garden level walls

       Gd	Good Exposure
       Av	Average Exposure (split levels or foyers typically score average or above)	
       Mn	Mimimum Exposure
       No	No Exposure
       NA	No Basement
```{r}
sum(is.na(feature$BsmtExposure)) 
```
- NA is no Basement.
- Catagory data


##"BsmtFinSF1"   
Type 1 finished square feet
```{r}
sum(is.na(feature$BsmtFinSF1)) 
summary(feature$"BsmtFinSF1") 
#csv1
feature1$"BsmtFinSF1"[is.na(feature$"BsmtFinSF1")]="missing"
summary(feature1$"BsmtFinSF1") 
sum(is.na(feature1$BsmtFinSF1)) 

feature2$"BsmtFinSF1"[is.na(feature$"BsmtFinSF1")] = 441.4
```
- Only 1 NA 
- replace with mean in the csv2

##"BsmtFinSF2"   
Type 2 finished square feet

```{r}
sum(is.na(feature$BsmtFinSF2)) 
```
- NA is no Basement.
- Catagory data

##"BsmtFinType1"
Rating of basement finished area

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement
```{r}
sum(is.na(feature$BsmtFinType1)) 
```
- NA is no Basement.
- Catagory data

##"BsmtFinType2"
Rating of basement finished area (if multiple types)

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement
```{r}
sum(is.na(feature$BsmtFinType2)) 
```
- NA is no Basement.
- Catagory data

##"BsmtFullBath" 
 Basement full bathrooms
```{r}
sum(is.na(feature$BsmtFullBath)) 
class((feature$BsmtFullBath))
#csv1
feature1$BsmtFullBath[is.na(feature$BsmtFullBath)]="missing"
summary(feature1$BsmtFullBath) 
sum(is.na(feature1$BsmtFullBath)) 
#csv2
feature2$"BsmtFullBath"[is.na(feature$"BsmtFullBath")] = 0
```
- Only 2 NA
- replace with 0

##"BsmtHalfBath" 
Basement half bathrooms
```{r}
sum(is.na(feature$BsmtHalfBath)) 
class(feature$BsmtHalfBath)
feature1$BsmtHalfBath[is.na(feature$BsmtHalfBath)]="missing"
summary(feature1$BsmtHalfBath) 
sum(is.na(feature1$BsmtHalfBath)) 
#csv2
feature2$BsmtHalfBath[is.na(feature$BsmtHalfBath)] = 0
```
- Only 2 NA


##"BsmtQual"     
Evaluates the height of the basement

       Ex	Excellent (100+ inches)	
       Gd	Good (90-99 inches)
       TA	Typical (80-89 inches)
       Fa	Fair (70-79 inches)
       Po	Poor (<70 inches
       NA	No Basement
```{r}
sum(is.na(feature$BsmtQual)) 
```
- NA is no Basement.
- Catagory data


##"BsmtUnfSF"  
Unfinished square feet of basement area
```{r}
sum(is.na(feature$BsmtUnfSF)) 
class(feature$BsmtUnfSF)
feature1$BsmtUnfSF = as.numeric(feature1$BsmtUnfSF)
feature1$BsmtUnfSF[is.na(feature$BsmtUnfSF)]="missing"
summary(feature1$BsmtUnfSF) 
sum(is.na(feature1$BsmtUnfSF)) 
#csv2
feature2$BsmtUnfSF[is.na(feature$BsmtUnfSF)] =560.8

```
- only 1 NA


##"CentralAir"   
```{r}
sum(is.na(feature$CentralAir)) 
```
- no NA
- good

##"Condition1" 
Proximity to various conditions
	
       Artery	Adjacent to arterial street
       Feedr	Adjacent to feeder street	
       Norm	Normal	
       RRNn	Within 200' of North-South Railroad
       RRAn	Adjacent to North-South Railroad
       PosN	Near positive off-site feature--park, greenbelt, etc.
       PosA	Adjacent to postive off-site feature
       RRNe	Within 200' of East-West Railroad
       RRAe	Adjacent to East-West Railroad
```{r}
sum(is.na(feature$Condition1)) 
summary(feature$"Condition1") 
```
- no NA
- good

##"Condition2"   
Proximity to various conditions (if more than one is present)
		
       Artery	Adjacent to arterial street
       Feedr	Adjacent to feeder street	
       Norm	Normal	
       RRNn	Within 200' of North-South Railroad
       RRAn	Adjacent to North-South Railroad
       PosN	Near positive off-site feature--park, greenbelt, etc.
       PosA	Adjacent to postive off-site feature
       RRNe	Within 200' of East-West Railroad
       RRAe	Adjacent to East-West Railroad
```{r}
sum(is.na(feature$Condition2)) 
```
- no NA
- good


##"Electrical" 
Electrical system

       SBrkr	Standard Circuit Breakers & Romex
       FuseA	Fuse Box over 60 AMP and all Romex wiring (Average)	
       FuseF	60 AMP Fuse Box and mostly Romex wiring (Fair)
       FuseP	60 AMP Fuse Box and mostly knob & tube wiring (poor)
       Mix	Mixed
```{r}
sum(is.na(feature$Electrical)) 
class(feature$Electrical)
#csv1
feature1$Electrical[is.na(feature$Electrical)]="missing"
summary(feature1$Electrical) 
sum(is.na(feature1$Electrical)) 
#csv2
feature2$Electrical[is.na(feature$Electrical)] = "FuseA"

```
- only 1 NA
- good


#save
```{r}
write.csv(feature1,"feature_JJC_1.csv")
write.csv(feature2,"feature_JJC_2.csv")
```

