---
title: "cleaning2"
author: "Jian Kang"
date: "11/15/2017"
output: html_document
---

Need transform:
Exterior1st
Exterior2nd
Foundation
GarageType


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data
```{r}
library(readr)
feature_KJ_2 <- read_csv("feature_KJ_1copy.csv")
feature_KJ_2 <- feature_KJ_2[, -1]
```


### EnclosedPorch
**Enclosed porch area in square feet**
- 2460 (84.3%) == 0
- Removed
```{r}
feature_KJ_2 <- feature_KJ_2[, -4]
```


### ExterCond
**Evaluates the present condition of the material on the exterior**
- No NA
- Ordinal values are set.
- Transform into numeric data


### ExterQual
**Evaluates the quality of the material on the exterior**
- No NA
- Ordinal values are set.
- Transform into numeric data


### Exterior1st
**Exterior covering on house**
- Catergorical, need transform
- 1 NA: "Other"


### Exterior2nd
**Exterior covering on house (if more than one material)**
- Catergorical, need transform
- 1 NA: "Other"


### Fence
**Fence quality**
- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### FireplaceQu
**Fireplace quality**
- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### Fireplaces
**Number of fireplaces**
- No NA
- Ordinal: 0, 1, 2, 3, 4


### Foundation
**Type of foundation**
- No NA
- Categorical -- need transform


### FullBath
**Full bathrooms above grade**
- No NA
- Ordinal: 0, 1, 2, 3, 4

### HalfBath
**Half baths above grade**
- No NA
- Ordinal: 0, 1, 2

#### Combined
#### "Bath = FullBath + 0.5*HalfBath"
```{r}
feature_KJ_2$Bath = feature_KJ_2$FullBath + 0.5*feature_KJ_2$HalfBath
feature_KJ_2 <- feature_KJ_2[ , !names(feature_KJ_2) %in% c("FullBath","HalfBath")]
```


### Functional
**Home functionality (Assume typical unless deductions are warranted)**
- 2 NA: mode (median)
- Ordinal: 0, 1, 2, 3, 4, 5, 6, 7


### GarageArea
**Size of garage in square feet**
- 1 NA: median
- Standardized

```{r}
feature_KJ_2$GarageArea = scale(feature_KJ$GarageArea)
```

### GarageCars
**Size of garage in car capacity**
- 1 NA: median
- Removed, and keep "GarageArea" instead.
```{r}
feature_KJ_2 <- feature_KJ_2[, -14]
```


### GarageCond
**Garage condition**
- Removed, and keep "GarageQual" instead.
```{r}
feature_KJ_2 <- feature_KJ_2[, -14]
```

### GarageFinish
**Interior finish of the garage**
- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### GarageQual
- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### GarageType
**Garage location**
- Categorical (not ordinal by plot)
- Need transformation


### GarageYrBlt
**Year garage was built**
- 159 NA: Min-1 = 1894
- One outlier: 2207! Maybe a typo for "2007" ("YearBuilt" = 2006)
- 

### GrLivArea
**Above grade (ground) living area square feet**
- No NA
- Standardized
```{r}
feature_KJ_2$GrLivArea = scale(feature_KJ$GrLivArea)
```

