---
title: "cleaning"
author: "Jian Kang"
date: "11/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data
```{r}
library(readr)
feature_KJ <- read_csv("feature_KJ.csv")
nrow(feature_KJ)
```


### EnclosedPorch
**Enclosed porch area in square feet**
```{r}
sum(is.na(feature_KJ$EnclosedPorch))   # = 0
sum(feature_KJ$EnclosedPorch == 0)   # = 2460
```
- No NA
- 2460 (84.3%) == 0
- To be removed or combined with other factors
- Can be combined with "OpenPorchSF", "3SsnPorch", and "ScreenPorch"

\n


### ExterCond
**Evaluates the present condition of the material on the exterior**
5. Ex	Excellent
4. Gd	Good
3. TA	Average/Typical
2. Fa	Fair
1. Po	Poor
```{r}
sum(is.na(feature_KJ$ExterCond))   # = 0
sum(feature_KJ$ExterCond == "NA")   # = 0

feature_KJ$ExterCond[feature_KJ$ExterCond == "Ex"] <- 4
feature_KJ$ExterCond[feature_KJ$ExterCond == "Gd"] <- 3
feature_KJ$ExterCond[feature_KJ$ExterCond == "TA"] <- 2
feature_KJ$ExterCond[feature_KJ$ExterCond == "Fa"] <- 1
feature_KJ$ExterCond[feature_KJ$ExterCond == "Po"] <- 0
feature_KJ$ExterCond <- as.numeric(feature_KJ$ExterCond)
```

- No NA
- Ordinal values are set.
- Transform into numeric data

\n

### ExterQual
**Evaluates the quality of the material on the exterior**
5. Ex	Excellent
4. Gd	Good
3. TA	Average/Typical
2. Fa	Fair
1. Po	Poor
```{r}
sum(is.na(feature_KJ$ExterQual))   # = 0
sum(feature_KJ$ExterQual == "NA")   # = 0

feature_KJ$ExterQual[feature_KJ$ExterQual == "Ex"] <- 4
feature_KJ$ExterQual[feature_KJ$ExterQual == "Gd"] <- 3
feature_KJ$ExterQual[feature_KJ$ExterQual == "TA"] <- 2
feature_KJ$ExterQual[feature_KJ$ExterQual == "Fa"] <- 1
feature_KJ$ExterQual[feature_KJ$ExterQual == "Po"] <- 0
feature_KJ$ExterQual <- as.numeric(feature_KJ$ExterQual)

cor.test(feature_KJ$ExterQual, feature_KJ$ExterCond)  #0.03
```
- No NA
- Ordinal values are set.
- Transform into numeric data


### Exterior1st
**Exterior covering on house**
- AsbShng	Asbestos Shingles
- AsphShn	Asphalt Shingles
- BrkComm	Brick Common
- BrkFace	Brick Face
- CBlock	Cinder Block
- CemntBd	Cement Board
- HdBoard	Hard Board
- ImStucc	Imitation Stucco
- MetalSd	Metal Siding
- Other	Other
- Plywood	Plywood
- PreCast	PreCast	
- Stone	Stone
- Stucco	Stucco
- VinylSd	Vinyl Siding
- Wd Sdng	Wood Siding
- WdShing	Wood Shingles

```{r}
#feature_KJ$Exterior1st <- as.character(feature_KJ$Exterior1st)
sum(is.na(feature_KJ$Exterior1st))   # 1
feature_KJ$Exterior1st[is.na(feature_KJ$Exterior1st)] <- "Other"
```

- Catergorical, need transform
- 1 NA: "Other"


### Exterior2nd
**Exterior covering on house (if more than one material)**
**Same with Exterior1st**
```{r}
sum(is.na(feature_KJ$Exterior2nd))   #1
feature_KJ$Exterior2nd[is.na(feature_KJ$Exterior2nd)] <- "Other"
```
- Catergorical, need transform
- 1 NA: "Other"
- Combine: Exter1st + Exter2nd


### Fence
**Fence quality**
- GdPrv	Good Privacy
- MnPrv	Minimum Privacy
- GdWo	Good Wood
- MnWw	Minimum Wood/Wire
- NA	No Fence

```{r}
sum(is.na(feature_KJ$Fence))   # 2348 -- "No Fence"

feature_KJ$Fence[feature_KJ$Fence == "GdPrv"] <- 4
feature_KJ$Fence[feature_KJ$Fence == "MnPrv"] <- 3
feature_KJ$Fence[feature_KJ$Fence == "GdWo"] <- 2
feature_KJ$Fence[feature_KJ$Fence == "MnWw"] <- 1
feature_KJ$Fence[is.na(feature_KJ$Fence)] <- 0
feature_KJ$Fence <- as.numeric(feature_KJ$Fence)
```

- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### FireplaceQu
**Fireplace quality**
- Ex	Excellent - Exceptional Masonry Fireplace
- Gd	Good - Masonry Fireplace in main level
- TA	Average - Prefabricated Fireplace in main living area or Masonry Fireplace in basement
- Fa	Fair - Prefabricated Fireplace in basement
- Po	Poor - Ben Franklin Stove
- NA	No Fireplace

```{r}
sum(is.na(feature_KJ$FireplaceQu))   # 1420 -- "No Fireplace"

feature_KJ$FireplaceQu[feature_KJ$FireplaceQu == "Ex"] <- 5
feature_KJ$FireplaceQu[feature_KJ$FireplaceQu == "Gd"] <- 4
feature_KJ$FireplaceQu[feature_KJ$FireplaceQu == "TA"] <- 3
feature_KJ$FireplaceQu[feature_KJ$FireplaceQu == "Fa"] <- 2
feature_KJ$FireplaceQu[feature_KJ$FireplaceQu == "Po"] <- 1
feature_KJ$FireplaceQu[is.na(feature_KJ$FireplaceQu)] <- 0
feature_KJ$FireplaceQu <- as.numeric(feature_KJ$FireplaceQu)
```

- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### Fireplaces
**Number of fireplaces**

```{r}
sum(is.na(feature_KJ$Fireplaces)) #0
feature_KJ$Fireplaces <- as.numeric(feature_KJ$Fireplaces)
```
- No NA
- Ordinal: 0, 1, 2, 3, 4


### Foundation
**Type of foundation**
- BrkTil	Brick & Tile
- CBlock	Cinder Block
- PConc	Poured Contrete	
- Slab	Slab
- Stone	Stone
- Wood	Wood

```{r}
sum(is.na(feature_KJ$Foundation))   #0
```

- No NA
- Categorical -- need transform


### FullBath
**Full bathrooms above grade**

```{r}
sum(is.na(feature_KJ$FullBath))   #0
summary(feature_KJ$FullBath)
```
- No NA
- Ordinal: 0, 1, 2, 3, 4
- Can be combined with "HalfBath"

### Functional
**Home functionality (Assume typical unless deductions are warranted)**
- Typ	Typical Functionality
- Min1	Minor Deductions 1
- Min2	Minor Deductions 2
- Mod	Moderate Deductions
- Maj1	Major Deductions 1
- Maj2	Major Deductions 2
- Sev	Severely Damaged
- Sal	Salvage only

```{r}
sum(is.na(feature_KJ$Functional))   #2
sum(feature_KJ$Functional == "NA")   # = 0

feature_KJ$Functional[feature_KJ$Functional == "Typ"] <- 7
feature_KJ$Functional[feature_KJ$Functional == "Min1"] <- 6
feature_KJ$Functional[feature_KJ$Functional == "Min2"] <- 5
feature_KJ$Functional[feature_KJ$Functional == "Mod"] <- 4
feature_KJ$Functional[feature_KJ$Functional == "Maj1"] <- 3
feature_KJ$Functional[feature_KJ$Functional == "Maj2"] <- 2
feature_KJ$Functional[feature_KJ$Functional == "Sev"] <- 1
feature_KJ$Functional[feature_KJ$Functional == "Sal"] <- 0

feature_KJ$Functional <- as.numeric(feature_KJ$Functional)
summary(feature_KJ$Functional)
#Take the mode (also median)
feature_KJ$Functional[is.na(feature_KJ$Functional)] <- 7
```

- 2 NA: mode (median)
- Ordinal: 0, 1, 2, 3, 4, 5, 6, 7


### GarageArea
**Size of garage in square feet**

```{r}
sum(is.na(feature_KJ$GarageArea))   #1
summary(feature_KJ$GarageArea)
feature_KJ$GarageArea[is.na(feature_KJ$GarageArea)] <- 480
```

- 1 NA: median
- Can be combined with "GarageCars"


### GarageCars
**Size of garage in car capacity**

```{r}
sum(is.na(feature_KJ$GarageCars))   #1
summary(feature_KJ$GarageCars)
feature_KJ$GarageCars[is.na(feature_KJ$GarageCars)] <- 2

cor.test(feature_KJ$GarageCars, feature_KJ$GarageArea)  #0.8896894
```

- 1 NA: median
- Can be removed, and keep "GarageArea" instead.


### GarageCond
**Garage condition**
5. Ex	Excellent
4. Gd	Good
3. TA	Average/Typical
2. Fa	Fair
1. Po	Poor
0. NA No Garage
```{r}
feature_KJ$GarageCond[feature_KJ$GarageCond == "Ex"] <- 5
feature_KJ$GarageCond[feature_KJ$GarageCond == "Gd"] <- 4
feature_KJ$GarageCond[feature_KJ$GarageCond == "TA"] <- 3
feature_KJ$GarageCond[feature_KJ$GarageCond == "Fa"] <- 2
feature_KJ$GarageCond[feature_KJ$GarageCond == "Po"] <- 1
feature_KJ$GarageCond[is.na(feature_KJ$GarageCond)] <- 0
feature_KJ$GarageCond <- as.numeric(feature_KJ$GarageCond)
```

- Can be removed, and keep "GarageQual" instead.


### GarageFinish
**Interior finish of the garage**
3. Fin	Finished
2. RFn	Rough Finished	
1. Unf	Unfinished
0. NA	No Garage
```{r}
sum(is.na(feature_KJ$GarageFinish))   #159
feature_KJ$GarageFinish[feature_KJ$GarageFinish == "Fin"] <- 3
feature_KJ$GarageFinish[feature_KJ$GarageFinish == "RFn"] <- 2
feature_KJ$GarageFinish[feature_KJ$GarageFinish == "Unf"] <- 1
feature_KJ$GarageFinish[is.na(feature_KJ$GarageFinish)] <- 0
feature_KJ$GarageFinish <- as.numeric(feature_KJ$GarageFinish)

cor.test(feature_KJ$GarageFinish, feature_KJ$GarageCond)  #0.48
```

- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### GarageQual
5. Ex	Excellent
4. Gd	Good
3. TA	Average/Typical
2. Fa	Fair
1. Po	Poor
0. NA	No Garage
```{r}
feature_KJ$GarageQual[feature_KJ$GarageQual == "Ex"] <- 5
feature_KJ$GarageQual[feature_KJ$GarageQual == "Gd"] <- 4
feature_KJ$GarageQual[feature_KJ$GarageQual == "TA"] <- 3
feature_KJ$GarageQual[feature_KJ$GarageQual == "Fa"] <- 2
feature_KJ$GarageQual[feature_KJ$GarageQual == "Po"] <- 1
feature_KJ$GarageQual[is.na(feature_KJ$GarageQual)] <- 0
feature_KJ$GarageQual <- as.numeric(feature_KJ$GarageQual)

cor.test(feature_KJ$GarageQual, feature_KJ$GarageCond)   #0.9466563

summary(lm(SalePrice ~ GarageCond, data = feature_KJ))
summary(lm(SalePrice ~ GarageQual, data = feature_KJ))
```

- NA is meaningful
- Ordinal values are set.
- Transform into numeric data


### GarageType
**Garage location**
- 2Types	More than one type of garage
- Attchd	Attached to home
- Basment	Basement Garage
- BuiltIn	Built-In (Garage part of house - typically has room above garage)
- CarPort	Car Port
- Detchd	Detached from home
- NA	No Garage

```{r}
feature_KJ$GarageType[is.na(feature_KJ$GarageType)] <- "NoGarage"
sum(is.na(feature_KJ$GarageType))
```

- Categorical (not ordinal by plot)
- Need transformation


### GarageYrBlt
**Year garage was built**
```{r}
sum(is.na(feature_KJ$GarageYrBlt))  #159
feature_KJ$GarageYrBlt[is.na(feature_KJ$GarageYrBlt)] <- 1894
feature_KJ$GarageYrBlt[feature_KJ$GarageYrBlt == 2207] <- 2007
```
- 159 NA: Min-1 = 1894
- One outlier: 2207! Maybe a typo for "2007" ("YearBuilt" = 2006)
- 

### GrLivArea
**Above grade (ground) living area square feet**
```{r}
sum(is.na(feature_KJ$GrLivArea))  #0
```

- No NA
- Numeric


### HalfBath
**Half baths above grade**

```{r}
sum(is.na(feature_KJ$HalfBath))  #0

cor.test(feature_KJ$HalfBath, feature_KJ$FullBath)  #0.16
```

- No NA
- Ordinal: 0, 1, 2
- Combine with "FullBath" ++ ??